DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-16 paper/paper.tex
college mails

\author{
\IEEEauthorblockN{Mohamed Shawky}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: mohamedshawky911@gmail.com} \\
\IEEEauthorblockN{Remonda Talaat}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: remondatalaat21@gmail.com}
\and
\IEEEauthorblockN{Mahmoud Adas}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: mido3ds@gmail.com} \\
\IEEEauthorblockN{Evram Youssef}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: evramyousef@gmail.com}
}

>>>>

\author{
\IEEEauthorblockN{Mohamed Shawky}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: mohamed.sabae99@eng-st.cu.edu.eg} \\
\IEEEauthorblockN{Remonda Talaat}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: Remonda.Bastawres99@eng-st.cu.edu.eg}
\and
\IEEEauthorblockN{Mahmoud Adas}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: mahmoud.ibrahim97@eng-st.cu.edu.eg} \\
\IEEEauthorblockN{Evram Youssef}
\IEEEauthorblockA{Computer Engineering\\
Cairo University\\
Email: evram.narouz00@eng-st.cu.edu.eg}
}
